### 2015-02-10 article.tex
add assign problem section

% !TeX spellcheck = en_US
\documentclass[]{TAACpaper}
\usepackage[linesnumbered,boxed]{algorithm2e}
\begin{document}

@@

Denote by $\delta(\vec{u},\vec{v})$ the Hamming distance between $\vec{u}$ and $\vec{v}$. Through $N_l(\vec{u})$ we denote the neighborhood of a point $\vec{u}$ radius $l$, ie:
\begin{align} 
& N_l(\vec{u})=\{\vec{v} \in E^{\eta}:\delta(\vec{u},\vec{v})\le l \}, l=\bar{1,\eta}
\end{align}

When $l=\eta$ a set $ N_l(\vec{u})$ for any vector $\vec{u}$ coincides with the set $E^{\eta}$ and being in this neighborhood vector with a minimum value of the objective function is equivalent to solving the original problem. The standard algorithm local search algorithm starts with a randomly selected vector $\vec{u^0}$.
On the $i$ step of the algorithm move from the current vector in the neighbouring that the minimum value of the objective function in the neighborhood of the given vector:
\begin{align} 
& F(\vec{u}^{i+1})=min\{F(\vec{v}):\vec{v} \in N_l(\vec{u}^i)\}
\end{align}

@@

\begin{algorithm}[H]
	\textbf{function TabuSearch}($u^0,l,p,h$) \\
	// Initialize variables:	\\
	$u^{opt} = u^0$
	$F^{opt} = F^0$
	$\phi^{0} =  \emptyset$
	$i=0$ \\
	\While{the breakpoint is not triggered }{
	   $N_l = N_l(u^i,\phi^i,p,h) $ \\
		\eIf{$N_l \ne   \emptyset $}{
			$ u^{i+1} = u^i$ \\
			$i = i + 1$ \\
			\textbf{goto} 5
		}
		{
			// find optimum into the neighbord $N_l$: \\
			$ u^{i+1} : F(u^{i+1}) = min\{ F(y): y \in N_l \}$
		}

@@

\caption{Pseudo-code for probabilistic tabu-search algorithm.}
\label{alg:TabuSearch}
\end{algorithm}

@@

\subsection{Analysis of the algorithm parameters}
Modified tabu search algorithm has 3 main parameters: $p$ -- the probability of hitting solutions in a neighborhood, $h$ -- size of the list of prohibitions and $N_{neighbors}$ -- accepted count limit of size of neighbordhood $N_l(\vec{u})$. For the experiments, we constructed the test tasks on the basis of the capacity routing problems developed by Breedam, Fisher, Christofides and Eilon. To determine trends in time and cost of the decision to use exponential smoothing by a factor of $0.1$.

@@

In this experiment we use two different breakpoint strategies: 
\begin{enumerate}
	\item $StepCount$ termination strategy --  terminates when an amount of steps has been reached;
	\item $TimeSpent$ termination strategy -- terminates when an amount of time has been used.
\end{enumerate}

As should have been expected, for large values of the parameter a jam occurs in local optimum due to the large number of restrictions of movement in space. Otherwise if you select a too small tabu size, algorithm can still get stuck in a local optimum. In the first computational experiment we made finding the best solutions for different values of the tabu size parameter from interval $h \in [0, 40]$ (pict. 1 an pict. 2).
\begin{figure}[h]
	\hfil\includegraphics[height=2.2in]{images/tabuSize_time}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the size of the tabu list when using $ TimeSpent $ termination strategy
	}
	\label{aba:fig3}
\end{figure}

@@

In the second experiment (see figure \ref{aba:fig4}) we built a relationship between the number $N_{neighborhood}$ of viewed solutions neighborhood size $N_l(\vec{u})$ using $TimeSpent$ termination strategy. In this experiment we made finding the best solutions for different values of the neighborhood size parameter from interval $N_{neighborhood} \in [750, 850]$ (pict. 1 an pict. 2).

@@

Modification of the scheme is based on the hypothesis of "On a large valley." According to this hypothesis, the average local optima are located much closer to the global than a randomly chosen point. There is a certain concentration of local optimum in a small part of the feasible region, which is figuratively called a large valley. If this assumption is true, then it is advisable to remember the best solutions and based on them design new original decision. We use this idea to solve the  Routing Courier Delivery Problem.

@@

	\textbf{function constructSolution}( $U^{opt}, p_u, n^{min}_s$) \\
	// $U^{opt}$ -- a sorted set array optimal solutions \\

@@

 \begin{equation} \label{anchor_points}
     \rho^j_i =  \dfrac{F(u^{opt}_1)}{avg[F(u^{opt}_k)]}, \forall k: \psi^j_k = \psi^j_i
 \end{equation}
 The number of anchor points $n_{\rho}$  is smaller than the set of optimal solutions, because a set of reference anchor points are removed the same point $(n_{\rho} \leq  n_u)$.

@@

 \begin{figure}[h]
 	\hfil\includegraphics[height=3.0in]{images/tabuSize_time.png}\hfil
 	\caption
 	{
 		The dependence of the quality of solutions and  the breaking point time by classic and modified algorithms using $ TimeSpent $ termination strategy
 	}
 	\label{aba:fig5}
 \end{figure}

@@

@@

\bibitem{jlogistics}  R. Shafeyev. Java-based framework for sloving routing problems.\\ url: http://jlogistics.net, 2015.

>>>>

% !TeX spellcheck = en_US
\documentclass[]{TAACpaper}
\usepackage[linesnumbered,boxed]{algorithm2e}
\pagestyle{plain}
\begin{document}

@@

Denote by $\delta(\vec{u},\vec{v})$ the Hamming distance between $\vec{u}$ and $\vec{v}$. Through $N_l(\vec{u})$ we denote the neighborhood of a point $\vec{u}$ radius $l$, ie \cite{vrp_shafeyev}:
\begin{align} 
& N_l(\vec{u})=\{\vec{v} \in E^{\eta}:\delta(\vec{u},\vec{v})\le l \}, l=\bar{1,\eta}
\end{align}

When $l=\eta$ a set $ N_l(\vec{u})$ for any vector $\vec{u}$ coincides with the set $E^{\eta}$ and being in this neighborhood vector with a minimum value of the objective function is equivalent to solving the original problem. The standard algorithm local search algorithm starts with a randomly selected vector $\vec{u^0}$.
On the $i$ step of the algorithm move from the current vector in the neighboring that the minimum value of the objective function in the neighborhood of the given vector:
\begin{align} 
& F(\vec{u}^{i+1})=min\{F(\vec{v}):\vec{v} \in N_l(\vec{u}^i)\}
\end{align}

@@

\begin{algorithm}[H]
	\textbf{function TabuSearch}($u^0,l,p,h$) \\
	// Initialize variables:	\\
	$u^{opt} = u^0$
	$F^{opt} = F^0$
	$\phi^{0} =  \emptyset$
	$i=0$ \\
	\While{the breakpoint is not triggered }{
	   $N_l = N_l(u^i,\phi^i,p,h) $ \\
		\eIf{$N_l \ne   \emptyset $}{
			$ u^{i+1} = u^i$ \\
			$i = i + 1$ \\
			\textbf{goto} 5
		}
		{
			// find optimum into the neighborhood $N_l$: \\
			$ u^{i+1} : F(u^{i+1}) = min\{ F(y): y \in N_l \}$
		}

@@

\caption{Pseudo-code for probabilistic Tabu Search algorithm.}
\label{alg:TabuSearch}
\end{algorithm}

@@

\subsection{Analysis of the algorithm parameters}
The Tabu Search algorithm has two main parameters: $h$ -- size of the list of prohibitions and $N_{neighbors}$ -- accepted count limit of size of neighbordhood $N_l(\vec{u})$. For the experiments, we constructed the test tasks on the basis of the capacity routing problems developed by Breedam, Fisher, Christofides and Eilon. To determine trends in time and cost of the decision we used exponential smoothing by a factor of $0.1$.

@@

In this experiment we use two different breakpoint strategies: 
\begin{enumerate}
	\item $StepCount$ termination strategy --  terminates when an amount of steps has been reached;
	\item $TimeSpent$ termination strategy -- terminates when an amount of time has been reached.
\end{enumerate}

As should have been expected, for large values of the parameter a jam occurs in local optimum due to the large number of restrictions of movement in space. Otherwise if you select a too small tabu size, algorithm can still get stuck in a local optimum. In the first computational experiment we made finding the best solutions for different values of the tabu size parameter from interval $h \in [0, 40]$ (pict. \ref{aba:fig2} an pict. \ref{aba:fig3}).
\begin{figure}[h]
	\hfil\includegraphics[height=2.2in]{images/tabuSize_time}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the size of the tabu list when using $ TimeSpent $ termination strategy
	}
	\label{aba:fig3}
\end{figure}

@@

In the second experiment (see figure \ref{aba:fig4}) we built a relationship between the number $N_{neigh.}$ of viewed solutions neighborhood size $N_l(\vec{u})$ using $TimeSpent$ termination strategy. In this experiment we made finding the best solutions for different values of the neighborhood size parameter from interval $N_{neigh.}\in[750, 850]$.

@@

Modification of the scheme is based on the hypothesis of "On a large valley"\cite{opt_Kochetov}. According to this hypothesis, the average local optima are located much closer to the global than a randomly chosen point. There is a certain concentration of local optimum in a small part of the feasible region, which is figuratively called a large valley. If this assumption is true, then it is advisable to remember the best solutions and based on them design new original decision. We use this idea to solve the  Routing Courier Delivery Problem.

@@

	\textbf{function constructSolution}( $U^{opt}, p_u, n^{min}_s$) \\
	// $U^{opt}$ -- a sorted set array of optimal solutions \\

@@

 \begin{equation} \label{anchor_points}
     \rho^j_i =  \dfrac{F(u^{opt}_1)}{avg[F(u^{opt}_k)]}, \forall k: \psi^j_k = \psi^j_i
 \end{equation}
 The number of anchor points $n_{\rho}$  is smaller than the set of optimal solutions, because a set of  anchor points are removed the same points $(n_{\rho} \leq  n_u)$.

@@

 \begin{figure}[h]
 	\hfil\includegraphics[height=3.0in]{images/tabu_mod.png}\hfil
 	\caption
 	{
 		The dependence of the quality of solutions and  the breaking point time by classic and modified algorithms using $ TimeSpent $ termination strategy
 	}
 	\label{aba:fig5}
 \end{figure}

@@

\bibitem{vrp_shafeyev} R.~Shafeyev ,L.~Lyubchik, A some realization of Tabu Search algorithm for Solving the Transportation Problem with Time Constraints // Vestnik NTU "KhPI". – Kharkov: NTU
"KhPI", 2013. – No3 (977). – p. 35–39.

\bibitem{jlogistics}  R. Shafeyev. Java-based optimixation framework for solving routing problems.\\ url: http://jlogistics.net, 2015.

@@
